Runaway and Hypervelocity Stars from Compact Object Encounters in Globular Clusters

### 2024-02-22 src/tex/ms.tex
Updated Zenodo DOI

We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://doi.org/10.5281/zenodo.7852916}.
We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.
The 2D position and proper motion distributions are separated into two different files, the conventions of which are described below.

>>>>

We include with this publication phase credible regions in phase space for ejecta populations from the MWGCs considered, which may be accessed at \url{https://doi.org/10.5281/zenodo.7599870}.
We intend these constructions to be used as secondary evidence for cluster membership of runaway stars, and to encourage further studies into understanding the respective phase space distributions.
The 2D position and proper motion distributions are separated into two different files, the conventions of which are described below.
